\section{Work}

\begin{experiencelist}
   \experienceitem
        {Founding Engineer}
        {Abbey Labs}
        {2022/07/25--2023/04/14}
    \begin{itemize}[noitemsep, topsep=0pt]
        \item
            Bootstrap the infrastructure to host complex data ingestion and workflow workloads.
        \item
            Rapidly prototype software demos to find product market fit.
    \end{itemize}

    \experienceitem
        {Software Engineer}
        {Meta}
        {2021/10/12--2022/07/22}
    \begin{itemize}[noitemsep, topsep=0pt]
        \item
            Implement Android camera hardware abstraction layer (HAL) for
            Meta Reality Labs AR/VR products.
        \item
            Develop Linux/Android native system services in C++ to support
            AR/VR use cases.
    \end{itemize}

    \experienceitem
        {Software Development Engineer II}
        {Amazon}
        {2020/11/30--present}
    \begin{itemize}[noitemsep, topsep=0pt]
        \item
            Implement and maintain a specialized workflow orchestration
            platform in Kotlin/Java to support Amazon Prime business.
        \item
            Manage AWS cloud infrastructure with Cloud Development Kit and
            CloudFormation.
    \end{itemize}

    \experienceitem{Software Engineer II}{Uber}{2019/03/18--2020/11/12}
    \begin{itemize}[noitemsep, topsep=0pt]
        \item
            Migrate a Python backend service to a gRPC Go service resulting in
            a 30x speedup.
        \item
            Lead the development of a new Go service that served the entire
            company's internal social media website. Set up and maintain
            infrastructure, CI, monitoring, and alerting.
    \end{itemize}

    \experienceitem
        {Systems Engineer}
        {Super Micro Computer}
        {2017/08/17--2019/03/08}
\end{experiencelist}
